Algorithmic and Economic Aspects of the Internet

### 2012-12-02 report/paper.tex
More report
Signed-off-by: Sam Phippen <samphippen@googlemail.com>

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

@@

\title{A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

>>>>

@@

\title{Algorithmic and Economic Aspects of the Internet}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Sam Phippen\titlenote{sp9857}\\
       \email{samphippen@googlemail.com}
% 2nd. author
\alignauthor
Luke Murray\titlenote{lm9131}
       \email{lm9131@bris.ac.uk}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}

For the assignment we attempted to implement the Adaptive
Aggressive\cite{Vytellingum:AA} trading agent strategy. Even with corrections
emailed by D. Cliff we found that our strategy does not trade as efficiently as
is implied in other background research\cite{DC:dominate}. In this paper we've
done a comparative analysis of the existing trading agents provided in BSE,
along with our implementation. We have also performed a post mortem analysis as
to why we believe that our trader is not trading as efficiently as expected.

We had initially set our sights on taking an implementation of AA and trying to
improve upon it, with a view to building something new and potentially more
effective, however, having found ourselves in a position where the agent is
nowhere near as effective as we expected, this was not a good springboard for
extension.

\end{abstract}

\section{Analysis of our agent with existing traders}

\subsection {Many versus many tests} For the analysis we started with a many
versus many test of our implementation versus each of the agents provided with
BSE. In this experiment we used the stepped supply and demand schedule provided
with an early version of the Bristol Stock Exchange, with three distinct time
periods, the first having prices in the range 10-190, the second in the range
200-300 and the third having prices in the same range as the first. In the many
versus many test 20 agents of each type were used (10 sellers and 10 buyers),
and the tests with this supply and demand schedule were repeated a total of 25
times.

The table below shows the number of rounds that our agent lost, the mean
difference in profit between the other agent and ours, and the standard
deviation of the difference in profit also.

\begin{center}
  \begin{tabular}{ l | l | l | l }
        Agent Type & Tests lost & $\Delta$ Profit Mean & $\Delta$ Profit StDev \\\hline
        Giveaway & 24 & 63.84 & 34.16\\
        ZIC & 25 & 75.38 & 36.15\\
        Shaver & 25 & 95.63 & 21.01\\
        Sniper & 25 & 22.67 & 12.78\\
        ZIP & 25 & 97.08 & 41.38\\
  \end{tabular}
\end{center}

In almost all of these cases our agent consistently generated a profit,
however when run against the Shaver agent, an oddity occurred. The agent on
average generated a loss which can be seen on the box plot in figure 1.

\begin{figure}[h!] 
\includegraphics[width=80mm]{box-plot-image.png}

\caption{Box plot of average profits of the 20 AA agents implemented by us in
the many vs many test against shaver agents. Box plot generated from:
http://www.alcula.com/calculators/statistics/box-plot/}
\end{figure}

-- insert explanation about that here.

\subsection{1 v 1 tests}
Given these initially dismal results, we decided that a good place to start a
detailed analysis would be a 1v1 test with the Giveaway trader, which is
clearly the worst of all the traders within the BSE system. 300 1v1 tests were
performed, we used the same schedule as the many versus many test. Results
where both bots made zero profit were eliminated, this brought the number of
tests included for analysis down from 300 to 242. Of these tests 103 were won
by Giveaway and 139 were won by our agent. The distributions of profit for each
agent, as well as the distribution of differences in profit can be seen in the
following histograms.

\begin{figure}[h!] \includegraphics[width=80mm]{giveaway_1_v_1.png}
\caption{Histogram of profit distributions over 300 similar trading runs for
the two bot types used in the 1v1 test. Note axis are different for the two
bots} \end{figure}

\begin{figure}[h!] \includegraphics[width=80mm]{giveaway_1_v_1_delta.png}
\caption {Histogram showing the difference between Giveaway and our AA implementation,
positive profit represents cases where Giveaway made more profit than AA}
\end{figure}

\newpage
Upon initially inspecting these graphs we had assumed that our agent should
lose to Giveaway, however we checked the medians of the distributions and noted
that the median profit of the Giveaway agent (1.7) was less than the median
profit (50.0) of our agent. We feel that this difference in profits is the
reason for our agent's overall victory against Giveaway. To determine if the
difference in medians is significant we decided to use the Wilcoxon signed-rank
test\cite{wiki:wilcoxon}. We like this test because:

\begin{enumerate}
\item It makes no assumptions about the underlying
distribution of profit pairs, as we can see from the histogram, these are
nowhere near normally distributed.

\item It handles the fact that the pairs are dependant but the individual runs
are independent.

\item We feel that the assumptions the distribution makes are fulfilled here:
the pairs do come from the same distributions. The pairs have been generated
largely at random by running different tests and collecting results. The data
are obviously ordinal as they are floating amounts of profit.

\end{enumerate}

In order to conduct this test we represented each run as a pair of
$(profit_{giveaway}, profit_{agent})$. The profits in the pair are taken from
the average profit column in the output of running BSE, so in fact the profit
values are divided by two, because their are two of each agent running in the
system. This will not effect the output of the test, as the change in magnitude
is the same for both agents. The test runs over the difference between the
first and second value in the pair. Our null hypothesis $H0$ is that the median
difference of each pair is zero, with our positive hypothesis $H1$ being that
the median difference of each pair is not zero. We performed the test using
scipy's built in Wilcoxon signed-rank test implementation\cite{scipy:wilcoxon}
and the results were extremely conclusive.  With $p=1.2\times10^{-6}$ we reject
$H0$ and conclude that the difference in medians is significant, as such the
profits generated by our agent are significantly better than Giveaway's.

This test was repeated for each of ZIC, Shaver, Sniper and ZIP. In each case
the results were that our bot performed significantly worse than the other agent (p < 0.01
in each case).

\subsection{One in many tests}
We also evaluated the agent initially in a one versus many test against a ZIC
trader which gave better results. Using a similar strategy above we started
with 25 tests to determine winners and average profits, however the results
were not totally conclusive, so we decided to generate some 300 experimental
results in order to attempt to draw conclusions about whether the bot performs
better in one v many tests. The results are shown below, using the same supply
and demand schedule, and two of our agent (1 buyer, 1 seller) and 20 of
the other agent (10 buyers, 10 sellers):

\begin{center}
\begin{tabular}{ l|l|l|l }
Agent Type & Tests lost & $\Delta$ Profit Mean & $\Delta$ Profit StDev \\
\hline
Giveaway & 157 & -2.28 & 86.95\\ 
ZIC & 225 & 52.86 & 83.99\\ 
Shaver & 287 & 76.36 & 46.06\\ 
Sniper & 256 & 19.49 & 16.74\\ 
ZIP & 234 & 64.76 & 89.76
\end{tabular}
\end{center}

We can see here that the agent performs better when trading on it's own than in
a small swarm.
